A Spatial AR System for Wide-area Axis-aligned Metric Augmentation of Planar Scenes

### 2021-11-09 paper/elsarticle/elsarticle-template.tex
paper

\paragraph{Virtual projector} The placement of the virtual projector determines from which pose the image to be projected is to \textit{appear} to have been projected.  We carry out this placement according to a small handful of steps. It is in accordance with the $X$- and $Y$-axes of the `downwards-facing' camera that we wish to place the $X$- and $Y$-axes of the augmentation; recognizing that a physical camera placed to face downwards is almost certain to not face downwards precisely, we first rotate the camera about its center of projection to align its optical axis\footnote{Strictly speaking, the optical axis is the back-projection of the principal point; in our usage, we understand it to refer to the ray through center of the image plane.} with the normal vector of the scene plane by applying the minimum arc-length rotation that relates the two, giving a \textit{virtual} camera facing directly downwards to the scene plane (cf.\ Figure~\ref{fig:virtualcam}). To obtain the virtual projector, we then (i) intersect the scene plane with the optical axis and rotate the projector's placement about that point of intersection, aligning the optical axis with the scene plane's normal vector and (ii) align the $X$- and $Y$-axes with those of the virtual camera. Finally, we (iii) translate along the scene plane's normal, in order to satisfy the desired projected image dimensions provided in metric units. These steps are illustrated in Figure~\ref{fig:virtualproj}. The resulting virtual projector is thus rendered fronto-parallel with the scene plane---enabling projection to the scene plane absent of projective distortions---and projects to the scene plane in the desired scale and with the the $X$- and $Y$-axes of the augmentation set in accordance with those of the `downwards-facing' camera. %\footnote{A physical camera placed to face downwards is almost certain to not face downwards precisely; in contrast, we align the virtual camera's optical axis exactly with the scene plane's normal vector, rendering it genuinely fronto-parallel with respect to the scene plane.}

It is thus in the sense that we set the $X$- and $Y$-axes of the virtual projector to the $X$- and $Y$-axes of the virtual camera that we place the horizontal and vertical axes of the desired augmentations `in accordance' with the horizontal and vertical image axes of the `downwards-facing' camera; the placement of the camera thereby intuitively determines the principal axes according to which augmentations are to be placed. Note further that a consequence of placing the virtual projector by rotating about the point of intersection of the projector's optical axis with the scene plane is that \textit{the center of the projector's image plane remains invariant} to the placement of the virtual projector. A steerable mirror can be aimed with respect to a point projected from the center of the projector's image plane, thereby facilitating placement.

>>>>

\paragraph{Virtual projector} The placement of the virtual projector determines from which pose the image to be projected is to \textit{appear} to have been projected.  We carry out this placement according to a small handful of steps. It is in accordance with the $X$- and $Y$-axes of the `downwards-facing' camera that we wish to place the $X$- and $Y$-axes of the augmentation; recognizing that a physical camera placed to face downwards is almost certain to not face downwards precisely, we first rotate the camera about its center of projection to align its optical axis\footnote{Strictly speaking, the optical axis is the back-projection of the principal point; in our usage, we understand it to refer to the ray through center of the image plane.} with the normal vector of the scene plane by applying the minimum arc-length rotation that relates the two, giving a \textit{virtual} camera facing directly downwards to the scene plane (cf.\ Figure~\ref{fig:virtualcam}). To obtain the virtual projector, we then (i) intersect the scene plane with the optical axis and rotate the projector's placement about that point of intersection, aligning the optical axis with the scene plane's normal vector and (ii) align the $X$- and $Y$-axes with those of the virtual camera. Finally, we (iii) translate along the scene plane's normal, in order to satisfy the desired projected image dimensions provided in metric units; the height $h_\text{proj}$ [m] above the ground plane at which the virtual projector is to be placed if the image---with original image width of $w_\text{im}$ [px]---is to be projected to the scene plane with a metric width of $w$ [m] is given by
\begin{equation}
h_\text{proj} = w \times f_\text{proj} / w_\text{im},
\end{equation}
where $f_\text{proj}$ [px] is the focal length of the projector. These three steps are illustrated in Figure~\ref{fig:virtualproj}. The resulting virtual projector is thus rendered fronto-parallel with the scene plane---enabling projection to the scene plane absent of projective distortions---and projects to the scene plane in the desired scale and with the the $X$- and $Y$-axes of the augmentation set in accordance with those of the `downwards-facing' camera. %\footnote{A physical camera placed to face downwards is almost certain to not face downwards precisely; in contrast, we align the virtual camera's optical axis exactly with the scene plane's normal vector, rendering it genuinely fronto-parallel with respect to the scene plane.}

It is thus in the sense that we set the $X$- and $Y$-axes of the virtual projector to the $X$- and $Y$-axes of the virtual camera that we place the horizontal and vertical axes of the desired augmentations `in accordance' with the horizontal and vertical image axes of the `downwards-facing' camera; the placement of the camera thereby intuitively determines the principal axes according to which augmentations are to be placed. Note further that a consequence of placing the virtual projector by rotating about the point of intersection of the projector's optical axis with the scene plane is that \textit{the center of the projector's image plane remains invariant} to the placement of the virtual projector. A steerable mirror can be aimed with respect to a point projected from the center of the projector's image plane, thereby further facilitating placement.
